A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-06-14 papers/execution-model/APLAS 2021/paper.tex
Add files via upload
Updating the introduction, the transition rules, and proofs

Building such oracles requires programmatic interfaces to implement the interactions. However, current blockchains often provide non-programmatic interfaces, such as the Ethereum JSON-RPC API and the Tezos RPC API. We present a typed API for invoking contracts from OCaml programs. Our type API supports the implementation of programs that safely interact with smart contracts on the blockchain. Such an API with a reliable computing facility and network connectivity is sufficient to self-provision an oracle. Moreover, our approach provides a type-safe facility instead of oracles, which are intrinsically untyped as they aim to provide a generic service.

@@

  \caption{Lifecycle transitions of a transaction}
  \label{fig:lifecycle-transaction}
\end{figure}
Figure~\ref{fig:lifecycle-transaction} shows the transitions to start
and finalize a transfer transaction, namely a smart contract invocation.
\TirName{Node-Inject} affects a local node and the blockchain. It
nondeterminstically selects a program that wants to do a transfer
operation. It
checks whether the sender of the transfer is a valid local account, whether
the balance is sufficient to pay the fee and the transferred amount,
whether there is an active transition for this sender (chkCount),
whether the public hash is associated with a smart contract, whether the type of the input parameter matchs with the smart contract's parameter type (chkArg), and whether the fee is
sufficient. If these conditions are fulfilled, the transition forges
an operation hash and returns it to the local node. 
The pending operation enters the pool and the sender's counter is set
to indicate an ongoing transition.

@@

Acceptance or rejection of a pending operation happens on the
blockchain independent of any local node. In our model, these
transitions are nondeterministic so that acceptance can happen any
time in the next 60 cycles \TirName{Block-Accept}. Afterwards, a
pending operation can only time out \TirName{Block-Timeout}.
If the transaction is accepted, then the sender's counter is reset,
the balances of sender and receiver are adjusted (updSucc), the smart contract storage and balance are updated (updConstr), and the time stamp increases.

@@

The proofs of these properties refer to all transitions with the detailed specifications of the related functions, such as chkCount and updSucc. Due to page limitations, not all transitions and their associated functions are presented in this paper, so the full proofs will be provided in an upcoming technical report. In this paper, since we only provide the proofs for Proposition 2 at 4 and 7.

>>>>

Building such oracles requires programmatic interfaces to implement the interactions. 
However, current blockchains often provide non-programmatic interfaces, 
such as the Ethereum JSON-RPC API and the Tezos RPC API. 
We present a typed API for invoking contracts from OCaml programs. 
Our typed API supports the implementation of application programs/ oracles 
that safely interact with smart contracts on the blockchain. 
Such an API with a reliable computing facility and network 
connectivity is sufficient to self-provision an oracle.
 Moreover, our approach provides a type-safe facility instead of oracles, 
 which are intrinsically untyped as they aim to provide a generic service.

@@

  \caption{Lifecycle transitions of a transaction}
  \label{fig:lifecycle-transaction}
\end{figure}
Figure~\ref{fig:lifecycle-transaction} shows the transitions to start
and finalize a transfer transaction, namely a smart contract invocation.
\TirName{Node-Inject} affects a local node and the blockchain. It
nondeterminstically selects a program that wants to do a transfer
operation. It
checks whether the sender of the transfer is a valid local account, whether
the balance is sufficient to pay the fee and the transferred amount,
whether there is an active transition for this sender (chkCount),
whether the public hash is associated with a smart contract on the blockchain, whether the type of the input parameter matchs with the smart contract's parameter type (chkArg), and whether the fee is
sufficient. If these conditions are fulfilled, the transition forges
an operation hash and returns it to the local node. 
The pending operation enters the pool and the sender's counter is set
to indicate an ongoing transition.

@@

Acceptance or rejection of a pending operation happens on the
blockchain independent of any local node. In our model, these
transitions are nondeterministic so that acceptance can happen any
time in the next 60 cycles \TirName{Block-Accept}. Afterwards, a
pending operation can only time out \TirName{Block-Timeout}.
If the transaction is accepted, then the sender's counter is reset,
the balances of sender is adjusted (updSucc), the smart contract's storage and balance are updated (updConstr), and the time stamp increases.

@@

The proofs of these properties refer to all transitions with the detailed specifications of the related functions, such as chkCount and updSucc. Due to page limitations, not all transitions and their associated functions are presented in this paper, so the full proofs will be provided in an upcoming technical report. In this paper, we only provide the proofs for Proposition 2 at items 4 and 7.
